Holomorphic field theories and higher algebra

### 2022-09-18 draft.tex
rephrased electric and magnetic theories

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.

@@

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, which we denote by
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in $V_Q = \sl(N)^{\oplus F}$, which we denote by
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation $V^*_Q = (\sl(N)^*)^{\oplus F}$, which we denote by
\[
\Tilde{Q} \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad \Tilde{R} \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}
\owen{I'm not sure I like this use of tilde for antiquarks}

The action functional is
\[
S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int \Tilde{R} \,\dbar_A \Tilde{Q},
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
We will denote this theory by $\cT(N,F)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, Q)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
\] 
\end{dfn}

@@

Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
The notion of duality can refer to several kinds of relationships,
but loosely speaking it means that some aspects of the two theories are equivalent under some dictionary or correspondence.
We will postpone saying something precise till we have some terminology in place.

We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
%Also, let $N_{\rm mes} \geq 0$ be some integer.  
%{\em Type A} holomorphic QCD is 
%\[
%\cT_{A} (N_c, N_f, N_{\rm mes},W) = \cT\left(G = \SU(N_c) \, , \, V = (\CC^{N_c})^{\oplus N_f} \, , \, Z = \CC^{\oplus N_{\rm mes}} \, , \, W\right) .
%\]

First, we have the `electric' theory which is the following holomorphic QCD
\[
\cT_{\sfE} (N_c , N_f) \define \cT\big(\SU(N_c) \, ,\, (\CC^{N_c})^{\oplus N_f} \, ,\, Z = 0 \, , \, W = 0\big) .
\]

%\begin{dfn}
%Suppose $\cT_A (N_c, N_f, N_{\rm mes}, W)$ is a type A holomorphic QCD. 
%Define the {\em dual} type A holomorphic QCD to be
%\[
%\Hat{\cT}_{A} (N_c, N_f, N_{\rm mes}, W) \define \cT_{A} (N_f - N_c, N_f, N_{\rm mes} + N_{f}^2 , W + 
%\]
%\end{dfn}

Second, we have the `magnetic' theory. 
In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
The magnetic theory is
\[
\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
\]
In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
Then the cubic polynomial $W$ is
\[
W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
\]

>>>>

We wish to study a holomorphic analog of supersymmetric chromodynamics.
We will call the relevant theory {\it QCD}, following convention, even though it is classical and not yet quantum.
We will specialize $G = SU(N)$ and so $G_\CC = SL(N)$.
The matter fields will consist of two types: quarks and antiquarks.
Let $V_N$ denote the {\em fundamental} (or defining) representation of $SL(N)$,
so $V_N = \CC^N$ with its natural left action.

@@

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V_Q = \Hom(\CC^F, V_N) \cong (V_N)^{\oplus F},
\] 
whose fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^*_Q = \Hom(V_N, \CC^F) \cong (V_N^*)^{\oplus F}, 
\]
whose fields are
\[
q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}

The action functional is
\[
S_{QCD} = \int B F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator. 
We will denote this theory by $\cT(N,F)$.\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{dfn}
A holomorphic QCD theory {\em with mesons}, denoted $\cT(N,F, V_M, W)$, is a holomorphic QCD with $N$ colors and $F$ flavors along with {\em meson fields}, which form a $\beta\gamma$ system valued in the vector space $V_M$, which we denote by
\[
M \in \Omega^{0,\bu}(\CC^2 , V_M) \quad\text{and}\quad N \in \Omega^{2,\bu}(\CC^2 , V_M^*) [1] .
\]
The action functional is
\[
S_{QCDwM} = S_{QCD} + \int N \,\dbar M + \int \d^2 z \; W(Q, \Tilde{Q}, M) .
\] 
\end{dfn}

@@

Our long-term goal is to show that two special cases of holomorphic QCD are {\em dual}.
The notion of duality can refer to several kinds of relationships,
but loosely speaking it means that some aspects of the two theories are equivalent under correspondence.
We will postpone saying anything precise till we have some terminology in place.

%We focus on the gauge group $G = \SU(N)$, and consider a class of holomorphic QCD theories associated to particular choices of representations and superpotential. 
%Following physics terminology, we will refer to the defining $N$-dimensional representation $\CC^N$ of $\SU(N)$ as the {\em fundamental} representation. 
%Also, let $N_c, N_f$ denote integers where $N_f \geq N_c \geq 2$.
%Also, let $N_{\rm mes} \geq 0$ be some integer.  
%{\em Type A} holomorphic QCD is 
%\[
%\cT_{A} (N_c, N_f, N_{\rm mes},W) = \cT\left(G = \SU(N_c) \, , \, V = (\CC^{N_c})^{\oplus N_f} \, , \, Z = \CC^{\oplus N_{\rm mes}} \, , \, W\right) .
%\]

Fix a positive integer $F$, for flavor.
There will be two theories. 
We call one side {\em electric} and the other {\em magnetic}.
The electric theory is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
{\it We restrict to $F \geq N \geq 2$.}
The magnetic theory is the holomorphic QCD with $\Tilde{N} = F-N$ colors and $F$ flavors, but with mesons $\Tilde{M}$ where $$\Tilde{V}_M = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\Tilde{W} =  \Tr(\Tilde{q} \Tilde{M}  \Tilde{Q}).$$
Again, we require $\Tilde{N} \geq 2$.
\owen{Please double-check that formula.}
%In this case the auxiliary vector space $Z$ is nontrivial (but transforms trivially under the gauge group as in the definition). 
%Our notation is $q,\Tilde{q}$ for elements of the vector spaces $V, \Bar{V}$ and $m\in Z$.
%The magnetic theory is
%\[
%\cT_{\sfM} (N_c, N_f) \define \cT\big(\SU(N_f - N_c) \, , \, (\CC^{N_f - N_c})^{\oplus N_f} \, , \, \CC^{\oplus N^2_f} \, , \, W = m q \Tilde{q} \big)
%\]
%In the definition of $W = m q \Tilde{q}$ we are using the natural contractions which we can describe explicitly as follows.
%Choose a basis $\{q_a^i\}$ for $V = (\CC^{N_f - N_c})^{\oplus N_f}$, $a = 1,\ldots, N_f - N_c$, $i=1,\ldots N_f$ and a dual basis $\{\Tilde{q}_i^a\}$ for $\Bar{V}$.
%Also, let $\{m_i^j\}$ be a basis for $\CC^{\oplus N_f^2}$. 
%Then the cubic polynomial $W$ is
%\[
%W = \sum_{i,j,a} m^i_j q_i^a \Tilde{q}^i_a .
%\]
